\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-12-15 manuscript.Rmd
Affiliation and abstract

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "4"
    email         : "j.v.duijnhoven1@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "5"
    email         : "l.j.m.schlangen@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

@@

  - name          : "Vineetha Kalavally"
    affiliation   : "6"
    email         : "vineetha@monash.edu"
    role:         
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "7, 8"
    email         : "celine.vetter@colorado.edu"
    role:         
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "9"
    email         : "gena.glickman@usuhs.edu"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "10"
    email         : "k.c.h.j.smolders@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 2, 3"
    email         : "manuel.spitschan@psy.ox.ac.uk"
    role:         
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
  - id            : "7"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "8"
    institution   : "Ximes GmbH, Frankfurt, Germany"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
  - id            : "11"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
  - id            : "*"
    institution   : "Joint first author"

@@

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

@@

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")

@@

                    A[label = '48 items were generataed by a robust expert panel'] 
                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52']
                    8[label = 'Measurement Invariance Analysis
                    Residual measurement invariance achieved']
                    9[label = 'Semantic Analysis']
                    10[label = 'LEBA Short Form (17 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
                fixedsize = true, fontsize = 38 ]
                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                    7[label = 'Rejected']
                    }

@@

#Histogram
#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])

@@

# Multivariate Normality
mardia <- psych::mardia(EFA.data, na.rm = T, plot =F)

@@

parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
  #Add lines connecting data points
  geom_line()+
    geom_line(data = Random.EV) +
  geom_line(data = Unadjusted.EV)+
    #Add the data points.
  geom_point(size=1)+
  geom_point(data = Random.EV, size=1)+
  geom_point(data = Unadjusted.EV, size=1)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
    #Add vertical line indicating parallel analysis suggested max # of factors to retain
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line()+
  geom_line(data = PA.Scree)+ 
  geom_point(size=1)+
  geom_point(data = PA.Scree, size=1)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
```

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
```

@@

@@

## Developing Short form of LEBA
We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017]. IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool. Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve \@ref(fig:itmeinfo) indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "F1")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "F3")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4",cex = .8)

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")

@@

```{r saveiteminfo, include=F}
jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v",ncol = 2)

@@

```{r IRTreliability, include=F}
#conditional reliability
F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )

@@

```{r shortIRT, include=FALSE}
F1 <- sem.data %>% 
  dplyr::select(item16, item36,  item17)
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item3,  item40)

@@

F5_fit.redu <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

@@

# Person Fit ####
## F1 Person fit ####
F1.personfit <- personfit(F1_fit) 
F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
rownames(F1.personfit_model_misfits)
nrow(F1.personfit_model_misfits)
hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)
F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme

@@

F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+
  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme

@@

F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme

@@

F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme

@@

F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics")+apatheme

@@

F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")

F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")

F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")

F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")

F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5")

@@

```{r savetestinfo, include=F, warning=F, message=F}
jpeg("Manuscript.figures/testinfo.png", width = 800, height = 750)
plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
          labels = "AUTO", label_size = 10, align = "v" )
dev.off()
```

@@

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))

@@

```{r}
library(WrightMap)
wrightMap(F1.estimation,F1_items.redu[,2])
wrightMap(F2.estimation,F2_items.redu[,2])
wrightMap(F3.estimation,F3_items.redu[,2])
wrightMap(F4.estimation,F3_items.redu[,2])
wrightMap(F5.estimation,F5_items.redu[,2])
```

>>>>

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "4, 5"
    email         : "j.v.duijnhoven1@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "5, 6"
    email         : "l.j.m.schlangen@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

@@

  - name          : "Vineetha Kalavally"
    affiliation   : "7"
    email         : "vineetha@monash.edu"
    role:         
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "8, 9"
    email         : "celine.vetter@colorado.edu"
    role:         
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "10"
    email         : "gena.glickman@usuhs.edu"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "5,6"
    email         : "k.c.h.j.smolders@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 12, 13"
    email         : "manuel.spitschan@tum.de "
    role:         
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
 - id            : "7"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
  - id            : "8"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"

  - id            : "9"
    institution   : "XIMES GmbH, Vienna, Austria"
  - id            : "10"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "11"
    institution   : "Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
  - id            : "12"
    institution   : "Technical University of Munich, Department of Sport and Health Sciences (TUM SG), Munich, Germany"
  - id            : "13"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
  - id            : "*"
    institution   : "Joint first author"

@@

abstract: |
  Light exposure is an important driver of health and well-being. Many aspects of light exposure are modulated by our behaviour. How these light-related behaviours can be shaped to optimise personal light exposure is currently unknown. Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behavior Assessment (LEBA). 
  An expert panel prepared the initial 48 item pool. Responses to these items were then collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones). Exploratory factor analysis on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime). Confirmatory factor analysis on another subset of participants (n=262) yielded the best fit for the five-factor solution after discarding another two items (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09). The internal consistency reliability coefficient for the total instrument was McDonald’s omega =0.73. Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05). Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690). 
  The psychometric properties of the LEBA instrument indicate the usability to measure the light exposure-related behaviours across a variety of settings and may offer a scalable solution to characterize light exposure-related behaviours in remote samples.

keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
wordcount         : "X"

@@

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")

@@

                    A[label = '48 items were generated by a robust expert panel'] 
                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52
                      Mcdonald  omega(total) for the total scale = .73']
                    8[label = 'Measurement Invariance Analysis
                    Residual measurement invariance achieved']
                    9[label = 'Semantic Analysis']
                    10[label = 'LEBA Short Form (17 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
                fixedsize = true, fontsize = 38 ]
                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                    7[label = 'Rejected']
                    }

@@

#Histogram
psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])

@@

# Multivariate Normality
mardia <- psych::mardia(EFA.data, na.rm = T, plot =T)

@@

parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
  #Add lines connecting data points
  geom_line()+
    #geom_line(data = Random.EV) +
  #geom_line(data = Unadjusted.EV)+
    #Add the data points.
  geom_point(size=3)+
  #geom_point(data = Random.EV, size=3)+
  #geom_point(data = Unadjusted.EV, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 48),breaks=seq(0,48,4))+
    #Add vertical line indicating parallel analysis suggested max # of factors to retain
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line()+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=3)+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(text = element_text(size = 25))  
```

@@

```{r MIdes, include=FALSE}

midata <- CFA.descriptives[,c(1:2,5:7)]
colnames(midata) <- c("Age", "Gender",  "Native_Speaker", "Work/School", "Mode" )
mides <- midata%>%
  tbl_summary(
    by = Native_Speaker,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,

    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
  modify_caption("Demographic Characteristics")

as_tibble(mides) -> mides_tibble 
as_kable_extra(mides, format = "latex",booktabs = T) -> mides_kable #save it as a knitr::kable

@@

## Developing Short form of LEBA
We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017]. IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool. Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve \@ref(fig:itmeinfo) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.

@@

# Plots ####
## F1 Plots ####
F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "F1: Wearing blue light filters OCC")
F1_info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
F1_iteminfo <- plot(F1_fit, type = "infotrace", 
                    facet_items = T, main = "F1: Wearing blue light filters")

## F2 Plots ####
F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "F2: Spending time outdoors OCC")
F2_info <- plot(F2_fit, type = "infoSE", main = "F2: Spending time outdoors")
F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2: Spending time outdoors")

## F3 Plots ####
F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "F3: Using phone and smart-watch in bed OCC")
F3_info <- plot(F3_fit, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
F3_iteminfo <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, main = "F3: Using phone and smart-watch in bed")

## F4 Plots ####
F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "F4: Using light before bedtime OCC")
F4_info <- plot(F4_fit, type = "infoSE", main = "F4: Using light before bedtime")
F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4: Using light before bedtime",cex = .8)

## F5 Plots ####
F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "F5: Using light in the morning and during daytime OCC")
F5_info <- plot(F5_fit, type = "infoSE", main = "F5: Using light in the morning and during daytime")
F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5: Using light in the morning and during daytime")

@@

```{r saveiteminfo, include=FALSE}
jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v",ncol = 2)

@@

```{r IRTreliability, include=FALSE}
#conditional reliability
F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )
F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
      main="" )

@@

```{r shortIRT, include=FALSE}
F1 <- sem.data %>% 
  dplyr::select(item16, item36,  item17)
F2.redu <- sem.data %>% 
  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
F3.redu <- sem.data %>% 
 dplyr::select(item27, item3,  item40)

@@

F5_fit.redu <- mirt(F5.redu, model = 1, itemtype = 'graded', SE = TRUE,
               Se.type = 'MHRM',technical = list(NCYCLES = 10000))

@@

# Person Fit ####
## F1 Person fit ####
F1.personfit <- personfit(F1_fit) 
F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
rownames(F1.personfit_model_misfits)
nrow(F1.personfit_model_misfits)
hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
abline(v = -2, lwd = 2, lty = 2)
F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme

@@

F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+
  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme

@@

F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme

@@

F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme

@@

F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme

@@

F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")

F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2: Spending time outdoors")

F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smart-watch in bed")

F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4: Using light before bedtime")

F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5: Using light in the morning and during daytime")

@@

```{r savetestinfo, include=FALSE, warning=F, message=F}
jpeg("Manuscript.figures/testinfo.png", width = 800, height = 750)
plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
          labels = "AUTO", label_size = 10, align = "v" )
dev.off()
```

@@

LEBA.Total <- LEBA.Total %>% 
  rowwise() %>% 
  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8, item9))

@@

```{r, warning=F, include=FALSE}
library(WrightMap)
library(RColorBrewer)
F1.e <- as.data.frame(F1.estimation)
F2.e <- as.data.frame(F2.estimation)
F3.e <- as.data.frame(F3.estimation)
F4.e <- as.data.frame(F4.estimation)
F5.e <- as.data.frame(F5.estimation)

estimation <- as.data.frame(cbind(F1.e,F2.e,F3.e,F4.e,F5.e))

threshold <- rbind(F1_items.redu[,2:5],
                   F2_items.redu[,2:5],
                   F3_items.redu[,2:5],
                   F4_items.redu[,2:5],
                   F5_items.redu[,2:5])

itemlevelcolors <- matrix(rep(brewer.pal(4, "Set1"), 18), byrow = TRUE, ncol = 4)

```{r WP, fig.cap="Person Item Map (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
library(WrightMap)
wrightMap(estimation, threshold, 
          item.prop = 0.65,

          main.title = "LEBA",
          dim.names = c("F1", "F2", "F3", "F4", "F5"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = T,
          dim.color = brewer.pal(5, "Set3"))
